<i>invivoPKfit</i> and <i>CvTdb</i> figures

### 2022-10-25 MainAnalysis.Rmd
Minor bug fixes

```{r, run_invivoPKfit, eval = FALSE}

@@

write.csv(PK.fit.table.1comp[[1]], "inst/ext/PK.fit.table.1comp.05092022.csv", row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], "inst/ext/processed.1comp.data.05092022.csv", row.names = FALSE)

write.csv(PK.fit.table.2comp[[1]], "inst/ext/PK.fit.table.2comp.05092022.csv", row.names = FALSE)
write.csv(PK.fit.table.2comp[[2]], "inst/ext/processed.2comp.data.05092022.csv", row.names = FALSE)

write.csv(PK.fit.table.flat[[1]], "inst/ext/PK.fit.table.flat.05092022.csv", row.names = FALSE)
write.csv(PK.fit.table.flat[[2]], "inst/ext/processed.flat.data.05092022.csv", row.names = FALSE)
```

>>>>

```{r, run_invivoPKfit, eval = TRUE}

THIS.DATE <- "102422"

@@

write.csv(PK.fit.table.1comp[[1]], paste("inst/ext/PK.fit.table.1comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.1comp[[2]], paste("inst/ext/processed.1comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)

write.csv(PK.fit.table.2comp[[1]], paste("inst/ext/PK.fit.table.2comp.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.2comp[[2]], paste("inst/ext/processed.2comp.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)

write.csv(PK.fit.table.flat[[1]], paste("inst/ext/PK.fit.table.flat.",THIS.DATE,".csv",sep=""), row.names = FALSE)
write.csv(PK.fit.table.flat[[2]], paste("inst/ext/processed.flat.data.",THIS.DATE,".csv",sep=""), row.names = FALSE)
```
